### 2019-01-10 tim-lucas-wsc.tex
Kate B edits.

We used two data sources that reflect malaria burden; point-prevalence surveys and polygon-level, aggregated incidence data. 
We selected Colombia and Madagascar as case examples as they both have good surveillance data.
The prevalence survey data were extracted from the Malaria Atlas Project prevalence survey database using only data from 1990 onwards \citep{bhatt2015effect, guerra2007assembling}.  % ceck todo
For Colombia we used all points from South America (n = 522) while for Madagascar we used only Malagasy data (n = 1505).
We chose these geographic regions based on a trade-off between wanting a large sample size but wanting data from geographically similar areas.
As the prevalence surveys cover different age ranges they were standardised to an age range of 2--10 using the model from \citep{smith2007standardizing}.
The polygon incidence data were collected from government reports and standardised using methods defined in \cite{cibulskis2011worldwide}.
This standardisation step accounts for missed cases due to lack of treatment seeking, missing case reports, and cases that sought medical attention outside the public health systems \citep{battle2016treatment}.
For reports where cases were not reported at the species level, national estimates of the ratio between \emph{Plasmodium falciparum} and \emph{P. vivax} cases were used to calculate \emph{P. falciparum} only cases. 
To minimise temporal effects we selected, for each country, one year of surveillance data. 
We used surveillance data from 2015 for Colombia (n = 952) and data from 2013 for Madagascar (n = 110) as these years had the most data in each case.

Raster surfaces of population for the years 2005, 2010 and 2015, were created using data from GPWv4 \citep{gpw4} and WorldPop \citep{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data. 
Population rasters for the remaining years were created by linear interpolation.

We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres that included the annual mean and log standard deviation of land surface temperature, enhanced vegetation index, mosquito temperature suitability index, elevation, tassel cap brightness, tassel cap wetness, log accessibility to cities, log night lights and proportion of urban land cover \cite{weiss2015re}. 
After preliminary analyses, tassel cap brightness and urban land cover were removed as they were highly correlated with other variables. 
The covariates were standardised to have a mean of zero and a standard deviation of one. 
These covariates were used for both the machine learning models and the polygon-level models.

For each region we fitted five models via caret \citep{caret}: elastic net \citep{enet}, Random Forest \citep{wright2015ranger}, projection pursuit regression \citep{friedman1981projection}, neural networks \citep{nnet} and boosted regression trees \citep{gbm}.
Our response variable was prevalence and we weighted the data by sample size (i.e. the number of people tested for malaria in each survey.
For each model we ran 5 fold cross-validation to select hyperparameters using random search for Random Forest and boosted regression trees and grid search for the other models. 
%The parameters tried can be seen in Table S1.
Predictions from these models were then made across Colombia and Madagascar.
These predictions were finally inverse logit transformed so that they are on the linear predictor scale of the top level model.

@@

@@

\begin{table}
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrr}
Cross-validation scheme & Country &  Covariates &  ML &  Covs + ML \\
\hline 
 Random &  Colombia &  0.45 &  \textbf{0.55} &  0.54 \\
 Random &  Madagascar &  0.70 &  \textbf{0.76} &  0.75 \\
 Spatial &  Colombia &  0.05 &  \textbf{0.18} &  0.10 \\
 Spatial &  Madagascar &  0.22 &  \textbf{0.63} &  0.61 
\end{tabular}
\label{t:results}
\end{table}

@@

Due to the low power of typical aggregated incidence datasets, previous analysis using disaggregation regression had to use a small number of covariates \citep{sturrock2014fine}.
However, the increased amount of data provided by using prevalence points, and the the fact that model such as Random Forest and elastic net can use many coviariates means future work could include many more covariates, potentially increasing predictive performance further.

@@

Our top-level polygon model is not technically stacking as we have not contrained the regression parameters to be positive nor included a sum-to-one constraint.
We did not include these constraints because the base models and the meta model are trained on response data on different scales.
However, future work could examine whether using a positive constraint on the regression parameters improves performance.

>>>>

We used two data sources that reflect malaria transmission; point-prevalence surveys and polygon-level, aggregated incidence data. 
We selected Colombia and Madagascar as case examples as they both have fairly complete surveillance data at a finer geographical resolution than admin 1.
The prevalence survey data were extracted from the Malaria Atlas Project prevalence survey database using only data from 1990 onwards \citep{bhatt2015effect, guerra2007assembling}.  % ceck todo
For Colombia we used all points from South America (n = 522) while for Madagascar we used only Malagasy data (n = 1505).
We chose these geographic regions based on a trade-off between wanting a large sample size but wanting data from geographically similar areas.
As the prevalence surveys cover different age ranges they were standardised to an age range of 2--10 using the model from \citep{smith2007standardizing}.
The polygon incidence data were collected from government reports and standardised using methods defined in \cite{cibulskis2011worldwide}.
This standardisation step accounts for missed cases due to lack of treatment seeking, missing case reports, and cases that sought medical attention outside the public health systems \citep{battle2016treatment}.
For reports where cases were not reported at the species level, national estimates of the ratio between \emph{Plasmodium falciparum} and \emph{P. vivax} cases were used to calculate \emph{P. falciparum} only cases. 
To minimise temporal effects we selected, for each country, one year of surveillance data. 
We used surveillance data from 2015 for Colombia (n = 952) and data from 2013 for Madagascar (n = 110) as these years had the most data in each case.

Raster surfaces of population for the years 2005, 2010 and 2015, were created using data from WorldPop \citep{tatem2017worldpop} and from GPWv4 \citep{gpw4} where WorldPop did not have values. 
Population rasters for the remaining years were created by linear interpolation.

We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres that included the annual mean and log standard deviation of land surface temperature, enhanced vegetation index, malaria parasite temperature suitability index, elevation, tassel cap brightness, tassel cap wetness, log accessibility to cities, log night lights and proportion of urban land cover \cite{weiss2015re}. 
After preliminary analyses, tassel cap brightness and urban land cover were removed as they were highly correlated with other variables. 
The covariates were standardised to have a mean of zero and a standard deviation of one. 
These covariates were used for both the machine learning models and the polygon-level models.

For each region we fitted five models via \emph{caret} \citep{caret}: elastic net \citep{enet}, Random Forest \citep{wright2015ranger}, projection pursuit regression \citep{friedman1981projection}, neural networks \citep{nnet} and boosted regression trees \citep{gbm}.
Our response variable was prevalence and we weighted the data by sample size (i.e. the number of people tested for malaria in each survey.
For each model we ran  five-fold cross-validation to select hyperparameters using random search for Random Forest and boosted regression trees and grid search for the other models. 
%The parameters tried can be seen in Table S1.
Predictions from these models were then made across Colombia and Madagascar.
These predictions were finally inverse logit transformed so that they are on the linear predictor scale of the top level model.

@@

\begin{table}[h!]
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrr}
Cross-validation scheme & Country &  Covariates &  ML &  Covs + ML \\
\hline 
 Random &  Colombia &  0.45 &  \textbf{0.55} &  0.54 \\
 Random &  Madagascar &  0.70 &  \textbf{0.76} &  0.75 \\
 Spatial &  Colombia &  0.05 &  \textbf{0.18} &  0.10 \\
 Spatial &  Madagascar &  0.22 &  \textbf{0.63} &  0.61 
\end{tabular}
\label{t:results}
\end{table}

@@

@@

Due to the low power of typical aggregated incidence datasets, previous analysis using disaggregation regression had to use a small number of covariates \citep{sturrock2014fine}.
However, as models such as Random Forest and elastic net are robust in the presence of high dimensional data, future work could include many more covariates, potentially increasing predictive performance further.

@@

While the approach presented here is related to stacking, it differs in that we have not constrained the regression parameters to be positive nor included a sum-to-one constraint i.e.\thinspace the result is not simply a weighted average of the level zero model predictions.
We did not include these constraints because the base models and the meta model are trained on response data on different scales.
However, future work could examine whether using a positive constraint on the regression parameters improves performance.
